An indexed construction of semi-cubical types

### 2021-05-31 paper/paper.tex
[paper] A bit of house-keeping

\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}

\usepackage[utf8x]{inputenc}
\usepackage{t1enc}

\usepackage{hyperref}
%\usepackage{proof}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{stmaryrd}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{color}
%\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{yfonts}
\usepackage[all]{xy}
\xyoption{2cell}
\UseAllTwocells

\makeatletter
\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
\makeatother

@@

\newcommand{\mkover}[1]{\widetilde{#1}}
\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
%\newcommand{\mkover}[1]{\dot{#1}}
%\newcommand{\mkprod}[3]{\Pi {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
%\newcommand{\mklam}[3]{\lambda {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mkapp}[2]{{#1}\,{#2}}
\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}

@@

%\newcommand{\mksigma}[3]{\Sigma {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
\newcommand{\mkfst}[1]{{#1}.1}
\newcommand{\mksnd}[1]{{#1}.2}
\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}

@@

\newcommand{\sort}[1]{\mathsf{U}_{#1}}
\newcommand{\univ}{\boxempty}
%\newcommand{\istype}{~:~S}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
%\newcommand{\mkeqtype}[3]{{#1} =_{#2} {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
%\newcommand{\reflterm}[1]{\textsf{refl}{#1}}
\newcommand{\reflterm}[1]{\widehat{#1}}
\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
%\newcommand{\reflterm}[1]{\lambda{#1}}
%\newcommand{\refltype}[1]{\lambda{#1}}
\newcommand{\refltype}[1]{\reflterm{#1}}
\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
%\newcommand{\rewlr}[2]{\mathsf{rew}^\rightarrow\;{#1}\;\mathsf{in}\;{#2}}
%\newcommand{\rewrl}[2]{\mathsf{rew}^\leftarrow\;{#1}\;\mathsf{in}\;{#2}}
\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
%\newcommand{\mktuple}[6]{\{#1\mapsto #3(#1); #2\mapsto #4(#2); #1\mapsto #5(#1); #2\mapsto #6(#2)\}}
\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
\newcommand{\opp}[1]{{#1}^{-1}}
\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}

@@

% Version basse
%% \newcommand{\appi}[2]{{#1}_{#2}}
%% \newcommand{\appidep}[2]{{#1}_{({#2})}}
%% \newcommand{\bp}[1]{{#1}_0}
%% \newcommand{\ep}[1]{{#1}_1}
%% \newcommand{\bpdep}[1]{{#1}_{(0)}}
%% \newcommand{\epdep}[1]{{#1}_{(1}}}
% Version haute
% \newcommand{\metaappi}[2]{{#1}_{[{#2}]}}
\newcommand{\appi}[2]{{#1}\;\!{#2}}
\newcommand{\appidep}[2]{{#1}_{#2}}
\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
\newcommand{\bpdep}[1]{{#1}_0}
\newcommand{\epdep}[1]{{#1}_1}

@@

\newcommand{\defeq}{\triangleq}
%\newcommand{\metaequiv}{=\!\!\!=}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
%\newcommand{\swap}[1]{\mathsf{swap}(#1)}
%\newcommand{\swapbracket}[1]{\mathsf{swap}(#1)}
%\newcommand{\swaptype}[1]{\mathsf{swap}(#1)}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

@@

\begin{document}

\title{An indexed construction of semi-cubical types}

\maketitle

@@

%\newcommand{\cubeovername}{cubeover}
%\newcommand{\Cubeovername}{Cubeover}
\newcommand{\cubeovername}{cube}
\newcommand{\Cubeovername}{Cube}
\newcommand{\pboxname}{box}
\newcommand{\pBoxname}{Box}

@@

%\newcommand{\heteroofliftbox}[3]{\mathsf{subliftBox}_{#1}^{#2,#3}}
%\newcommand{\heteroofliftlayer}[3]{\mathsf{subliftLayer}_{#1}^{#2,#3}}
%\newcommand{\heteroofliftcube}[3]{\mathsf{subliftCube}_{#1}^{#2,#3}}

@@

%\newcommand{\downboxleft}{\mathsf{subbox}^L}
%\newcommand{\downboxright}{\mathsf{subbox}^R}
%\newcommand{\downlayerleft}{\mathsf{sublayer}^L}
%\newcommand{\downlayerright}{\mathsf{sublayer}^R}
%\newcommand{\downcubeleft}{\mathsf{sub\cubeovername}^L}
%\newcommand{\downcuberight}{\mathsf{sub\cubeovername}^R}
%% \newcommand{\downboxleft}{\downarrow^{\mathsf{box},L}}
%% \newcommand{\downboxright}{\downarrow^{\mathsf{box},R}}
%% \newcommand{\downlayerleft}{\downarrow^{\mathsf{layer},L}}
%% \newcommand{\downlayerright}{\downarrow^{\mathsf{layer},R}}
%% \newcommand{\downcubeleft}{\downarrow^{\mathsf{cube},L}}
%% \newcommand{\downcuberight}{\downarrow^{\mathsf{cube},R}}
\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdep{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdep{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdep{\homoname}\cubeovername}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
%\newcommand{\downboxtypelarge}[1]{\mathsf{Subbox'}_{#1}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
%\newcommand{\cohboxtypelarge}[1]{\mathsf{Cohbox'}_{#1}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{full{\homoname}cube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

@@

\newcommand{\reflbox}[1]{\mathsf{reflbox}_{#1}}
\newcommand{\refllayer}[1]{\mathsf{refllayer}_{#1}}
\newcommand{\reflcube}[1]{\mathsf{reflcube}_{#1}}
\newcommand{\permutebox}{\mathsf{permutebox}}
\newcommand{\diagbox}{\mathsf{diagbox}}
\newcommand{\connbox}{\mathsf{connbox}}
%% \newcommand{\cohbox}{\mathsf{coh}^{\mathsf{box}}}
%% \newcommand{\cohlayer}{\mathsf{coh}^{\mathsf{layer}}}
\newcommand{\hd}{\mathsf{hd}}
\newcommand{\tl}{\mathsf{tl}}
\newcommand{\first}{\mathsf{first}}
\newcommand{\groupoid}{\mathsf{groupoid}}
\newcommand{\groupoidn}{\mathsf{groupoidn}}
\newcommand{\letinsplit}[3]{\!\!\begin{array}{l}\mathbf{let}~{#1}=#2\;\mathbf{in}~\\#3\end{array}}

@@

@@

\section{Introduction}

\section{Semi-cubical sets}
\label{sec:truncated-cubical-sets}

@@

The definition is dispatched over
Figures~\ref{fig:barecubicalsetstructurecore},
\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and
\ref{fig:barecubicalsetcoherences}. It describes the structure of the
underlying higher-dimensional relations on which cubes and boxes are
built, together with the definition of homogeneous $n$-boxes,
homogeneous $n$-cubes, together with face operations on boxes and
cubes, together with commutation properties of the face
operations. All are mutually defined as types of the target language
ETT. Note that such relational structure, cubes and boxes are relative
to a universe.

Note the presence of a coherence condition $\cohbox{l}{}$ to
ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$
are in the same type. The proof of $\cohbox{l}{}$ itself requires
an higher-dimensional coherence condition which we obtain by
working here in ETT where all proofs of an
equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many 
higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a
discussion on the de facto need for recursive higher-dimensional
coherence conditions in formulating higher-dimensional structures in
type theory). Note also that for a given
$n$, the coherence conditions evaluate to a reflexivity proof, so that
the construction evaluates to an effective sequence of types of
iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.

@@

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}\\
\\
\partialcubset{l}{n} && : & \sort{l+1}\\
\partialcubset{l}{0} && \defeq & \unittype\\
\partialcubset{l}{n'+1} && \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}\\
\\
\mycubsetcomp{l}{n} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
\mycubsetcomp{l}{n} & D & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}\\
\end{array}
$
}}
\caption{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
\label{fig:barecubicalsetstructurecore}
\end{figure*}

>>>>

\documentclass[a4paper]{article}

\usepackage{hyperref, fullpage, amssymb, stmaryrd, url, color, amsmath}
\usepackage{bookmark, fontspec}
\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false,doi=false]{biblatex}

% Add biblio-en.bib to the database
\addbibresource{biblio-en.bib}

\makeatletter
\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
\makeatother

@@

\newcommand{\mkover}[1]{\widetilde{#1}}
\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
\newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mkapp}[2]{{#1}\,{#2}}
\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}

@@

\newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
\newcommand{\mkfst}[1]{{#1}.1}
\newcommand{\mksnd}[1]{{#1}.2}
\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}

@@

\newcommand{\sort}[1]{\mathsf{U}_{#1}}
\newcommand{\univ}{\boxempty}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
\newcommand{\reflterm}[1]{\widehat{#1}}
\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
\newcommand{\refltype}[1]{\reflterm{#1}}
\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
\newcommand{\opp}[1]{{#1}^{-1}}
\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}

@@

\newcommand{\appi}[2]{{#1}\;\!{#2}}
\newcommand{\appidep}[2]{{#1}_{#2}}
\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
\newcommand{\bpdep}[1]{{#1}_0}
\newcommand{\epdep}[1]{{#1}_1}

@@

\newcommand{\defeq}{\triangleq}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

@@

@@

\newcommand{\cubeovername}{cube}
\newcommand{\Cubeovername}{Cube}
\newcommand{\pboxname}{box}
\newcommand{\pBoxname}{Box}

@@

@@

\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdep{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdep{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdep{\homoname}\cubeovername}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{full{\homoname}cube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

@@

\newcommand{\reflbox}[1]{\mathsf{reflbox}_{#1}}
\newcommand{\refllayer}[1]{\mathsf{refllayer}_{#1}}
\newcommand{\reflcube}[1]{\mathsf{reflcube}_{#1}}
\newcommand{\permutebox}{\mathsf{permutebox}}
\newcommand{\diagbox}{\mathsf{diagbox}}
\newcommand{\connbox}{\mathsf{connbox}}
\newcommand{\hd}{\mathsf{hd}}
\newcommand{\tl}{\mathsf{tl}}
\newcommand{\first}{\mathsf{first}}
\newcommand{\groupoid}{\mathsf{groupoid}}
\newcommand{\groupoidn}{\mathsf{groupoidn}}
\newcommand{\letinsplit}[3]{\!\!\begin{array}{l}\mathbf{let}~{#1}=#2\;\mathbf{in}~\\#3\end{array}}

@@

\title{An indexed construction of semi-cubical types}
\author{Hugo Herbelin}
\author{Ramkumar Ramachandra}

\begin{document}
\maketitle

@@

\section{Introduction}
\section{Semi-cubical sets}
\label{sec:truncated-cubical-sets}

@@

The definition is dispatched over Figures~\ref{fig:barecubicalsetstructurecore}, \ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}. It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations. All are mutually defined as types of the target language ETT. Note that such relational structure, cubes and boxes are relative to a universe. Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type. The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory). Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.

@@

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}                                                     \\
          \\
          \partialcubset{l}{n}    &                          & :      & \sort{l+1}                                               \\
          \partialcubset{l}{0}    &                          & \defeq & \unittype                                                \\
          \partialcubset{l}{n'+1} &                          & \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D) \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}                                                \\
          \\
          \mycubsetcomp{l}{n}     & (D:\partialcubset{l}{n}) & :      & \sort{l}                                                 \\
          \mycubsetcomp{l}{n}     & D                        & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}                        \\
        \end{array}
      $
    }}
  \caption{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
  \label{fig:barecubicalsetstructurecore}
\end{figure*}
